Maenpuen *et al.* --American Journal of Botany-- Appendix S1

### 2022-06-21 ms/response_letter_2.Rmd

---
geometry: margin=1in
link-citations: yes
#csl: templates/xxxx.csl
#bibliography: xxxx.bib
fontsize: 12pt
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{lineno}
 # - \linenumbers
output:
  pdf_document:
    keep_md: false
    fig_caption: yes
    keep_tex: no
    toc: no
    number_sections: no
    template: templates/eisvogel2.tex
    #template: null
    pandoc_args:
      - "--filter"
      - "pandoc-crossref"
  word_document:
    fig_width: 6
    fig_caption: yes
    toc: FALSE
    reference_docx: templates/rmd_style.docx
    pandoc_args:
    - "--filter"
    - "pandoc-crossref"
    - "--mathml"
---

Dear Editors,

We hereby resubmit the manuscript (AJB-D-21-00391R1), “Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)” (Phisamai Maenpuen, Masatoshi Katabuchi, Yusuke Onoda, Cong Zhou, Jiao-Lin Zhang, Ya-Jun Chen).
We thank the associate editor and the reviewers for their careful attention to detail in our manuscript and for providing comments that have greatly improved the study.

First, we found small errors in R codes and the total number of individuals used in our analysis was increased from 1365 to 1469.
Accordingly, several statistical values have changed slightly (highlighted in blue).
Second, we have cited one more R package that made a significant contribution to workflow management (Line 233-234).
Finally, we would like add Masatoshi Katabuchi as co-first author, if the journal does not have the limitation for this arrangement.

@@

Thank you again for the positive evaluation.

> Reviewer #1: Review of AJB-D-21-00391_R1

> Overall summary: The authors did a really nice job updating this manuscript in response to the previous reviews. I especially appreciate the inclusion of the section "Conversion between whole-leaf and leaf disc LMA". I also appreciate the updated appendices, which very much help to clarify the experimental design. I just have a few lingering comments, the only major one being about the new section (see comment on lines 311-317):

We are pleased that the reviewer was satisfied with the revised manuscript.
We also thank you for pointing out typos and style errors.

@@

> Line 123: it would be helpful to rephrase this line to clarify what unit is being reported here. For example: "We collected leaves from ___individuals of 334 species from 4 biomes"

Thank you.
We have added the number of individuals (Line 124).

> Line 139-143 Please report the # of individuals and # of species for each of the two datasets here

Thank you for pointing this error out.
We have added the numbers of species and individuals (Line 143-145).

@@

> In the Materials and Methods section please provide the city, spelled-out state (if in USA), and country for the locations and companies mentioned (such as L175).

Confirmed:
We have spelled-out state (Ohio) (Line 177).

> Would you like to thank the reviewers in the acknowledgements? It is not required, but we recommend it, especially if you found their comments helpful. (They don’t, as a rule, see your final response letter.)

Confirmed:
We have added a new line for the acknowledgements (line 380-381).

@@

> Data Availability:
> Please provide a doi for your data deposited in the Zenodo database at this time.

> For more information, see “Data Availability” at https://bsapubs.onlinelibrary.wiley.com/hub/journal/15372197/homepage/forauthors#epec and “g. Data Availability Statement” at https://bsapubs.onlinelibrary.wiley.com/hub/journal/15372197/homepage/forauthors#ps

Confirmed.
We have added the DOI: https://doi.org/10.5281/zenodo.6665083 (Line 397-398)

### 2022-06-21 ms/LMA_method.tex
update contribtuions and acknowledgment

Phisamai Maenpuen\textsuperscript{1,2,3},
Masatoshi Katabuchi\textsuperscript{1*},
Yusuke Onoda\textsuperscript{4},
Cong Zhou\textsuperscript{1,2},
Jiao-Lin Zhang\textsuperscript{1,3*},
Ya-Jun Chen\textsuperscript{1,3,5}

@@

We thank the editors and two anonymous reviewers, whose comments greatly improved the manuscript.
We also thank Lian-Bin Tao and Peng-Yun Yan for field work in China.
The data collection in Yakushima was achieved with help of many colleagues in particular Kenshi Tetsuka and financially supported by the Global COE Program `Asian conservation ecology', MEXT of Japan for Tetsukazu Yahara.
This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS `Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068), and Yunnan Revitalization Talents Support Plan (YNWR-QNBJ-2019-177).
PM was supported by financial support from CAS-TWAS President's Fellowship for International Doctoral Students.
MK was supported by CAS President's International Fellowship Initiative (2020FYB0003).

>>>>

Phisamai Maenpuen\textsuperscript{1,2,3*},
Masatoshi Katabuchi\textsuperscript{1*},
Yusuke Onoda\textsuperscript{4},
Cong Zhou\textsuperscript{1,2},
Jiao-Lin Zhang\textsuperscript{1,3},
Ya-Jun Chen\textsuperscript{1,3,5}

@@

We thank the editors and two anonymous reviewers, whose comments greatly improved the manuscript.
We also thank Lian-Bin Tao and Peng-Yun Yan for field work in China.
This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS `Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068), and Yunnan Revitalization Talents Support Plan (YNWR-QNBJ-2019-177).
The data collection in Yakushima was achieved with help of many colleagues in particular Kenshi Tetsuka and financially supported by the Global COE Program `Asian conservation ecology', MEXT of Japan for Tetsukazu Yahara.
PM was supported by financial support from CAS-TWAS President's Fellowship for International Doctoral Students.
MK was supported by CAS President's International Fellowship Initiative (2020FYB0003).
